\thesistitle

### 2019-04-10 main.tex
Clone contexts

\chapter{Background}
\section{Clone contexts}
Code clones can be found anywhere in the code. The most commonly studied type of clone is the method-level clone. Method-level clones are duplicated blocks of code in the body of a method. Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sysiphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}). The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.

A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information. First of all, the study that is referenced uses a very small dataset (460 copy & paste instances by 11 participants). Secondly, the group of subject only consists og IBM researchers (selection bias). Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code. Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper. Because of this, there is no reliable overview of how many clones there are in different contexts.

@@

\section{Clone types}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and less subtle. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

>>>>

\chapter{Background}
\section{Clone Class}

\section{Clone Contexts}
Code clones can be found anywhere in the code. The most commonly studied type of clone is the method-level clone. Method-level clones are duplicated blocks of code in the body of a method. Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sisyphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}). The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.

A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information. First of all, the study that is referenced uses a very small dataset (460 copy \& paste instances by 11 participants). Secondly, the group of subject only consists og IBM researchers (selection bias). Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code. Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper. Because of this, there is no reliable overview of how many clones there are in different contexts.

@@

\subsection{Clone refactoring in relationship to its context}
How to refactor clones is highly dependent on their context. Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class. If a method level clone is duplicated among classes in the same inheritance structure, we might need to pull-up a method in the inheritance structure. If instances of a method level clone are not in the same inheritance structure, we might need to either make a static method or create an inheritance structure ourselves. So not only a single instance of a clone has a context, but also the relationship between individual instances in a clone class. This is highly relevant to the way in which the clone has to be refactored.

\section{Clone Types}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and less subtle. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
